Study of the hadronization of charged pions

### 2016-10-06 chap5.tex
Corrections of chapter 5

This chapter treats of the analysis of the data taken in CLAS for the 
experiments E-02-104 \cite{Brooks:2002aa} and E-02-110 \cite{Hafidi:2002aa}.
The code name for the run is {\it eg2}, it was composed of three phases 
labeled {\it a}, {\it b} and {\it c}. The analysis is performed on the data 
collected in the beginning of 2004 during the third phase ({\it eg2c}), for 
which the beam energy was 5.014 GeV\footnote{The other phases gave a small 
amount of data at a beam energy of 4 GeV.}.

@@

The analysis of the experiment E-02-110, focusing on the study of color 
transparency effects, has been approved recently \cite{ElFassi:2008}. As this 
analysis went through a careful review by the CLAS collaboration, we use
similar analysis methods when possible. In particular, the electron selection 
presented here is very similar to theirs; the main difference being a new 
target determination method.

@@

To select electrons, we also require that the particles are negatively charged, 
according to the bending direction of the tracks in the drift chamber.
Positively charged particles are identified as positrons. In the rest of the 
analysis we use events with only one electron and no positron to avoid any 
confusion between the scattered electron and electrons from hadronic decays or 
photon conversion to $e^+e^-$ pair, which often lead to the production of a
positron.

@@

These cuts permit to minimize the kaon contamination, below 2.5~GeV/c, and the 
proton contamination for all momentum. The kaon contribution cannot be avoided, however 
it should remain a small contribution ($\sim$ 3\% according to simulation) 
with only a small effect on the final results (see section \ref{SysId} 
for details). Because protons could lead to even more contamination than kaons, 
a stricter cut is used at high momentum. This cut is also justified by 
HERMES data \cite{Airapetian:2007vu}, which show a very 
different behavior of the protons compared to the other hadrons (see chapter \ref{chap:data}).

@@

\begin{table}[p]
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Target & Carbon & Al (1) & Al (2) & Iron   & Tin    & Lead   \\ 
    \hline \hline
    Liquid & -30.1  & n/a    & n/a    & -30.2  & -30.1  & -30.1  \\ 
    Solid  & -24.7  & -25.0  & -23.8  & -24.9  & -23.8  & -24.9  \\
    \hline
  \end{tabular}
  \caption{Measured mean vertex position of targets, relative to the center of 
           CLAS (in cm). (Aluminum data are separated in two sets because the 
           target position appears to have changed at some point.)}
  \label{tab:targets}
\end{table}

@@

Since we are interested in deep inelastic scattering, we use the following 
cuts: $Q^2 > 1$~GeV$^2$/c$^2$ and $W > 2$~GeV. We also apply a cut $y < 0.85$ to 
reduce the impact of radiative effects, which will be discussed in more details in 
the section \ref{RadCor}.

@@

Once the identification is done, the calculation of the observables is 
straight forward and the statistical errors are calculated with this expression

\begin{equation}
{\delta \left ( R_A^h \right ) \over R_A^h} = \sqrt{ 1 /N_A^h + 1/ N_A^e +1/N_D^h + 1/N_D^e}
\end{equation}
and
\begin{equation}
\left ( \delta \left ( \Delta \langle P_\perp^2 \rangle \right ) \right )^2 = 
   \left ({\langle P_\perp^4 \rangle - \langle P_\perp^2 \rangle ^2}\right )_A / N_A^h
 + \left ({\langle P_\perp^4 \rangle - \langle P_\perp^2 \rangle ^2}\right )_D / N_D^h.
\end{equation}

The implementation of acceptance and radiative corrections is done through weights
given to each particles depending on its kinematic. The multiplicity ratio becomes

\begin{equation}
R_A^h (Q^2,\nu,z_h,P_\perp^2) = {{\sum \omega_A^h (Q^2,\nu,z_h,P_\perp^2) / \sum \omega_A^e (Q^2,\nu)} 
                       \over {\sum \omega_D^h (Q^2,\nu,z_h,P_\perp^2) / \sum \omega_D^e (Q^2,\nu)}},
\end{equation}
with $\omega$ the weights and all the sums running over all measured particles.
The expression for the transverse momentum broadening remains
\begin{equation}
\Delta \langle P_\perp^2 \rangle = \langle P_\perp^2 \rangle_A - \langle P_\perp^2 \rangle_D,
\end{equation}
but with
\begin{equation}
\langle P_\perp^2 \rangle = {\sum P_\perp^2 \times \omega (Q^2,\nu,z_h,P_\perp^2) \over \sum \omega (Q^2,\nu,z_h,P_\perp^2)}.
\end{equation}

This expressions leads to new expressions for the statistical error uncertainties:

\begin{equation}
{\delta \left ( R_A^h \right ) \over R_A^h} = 
      \sqrt{ \left ( {\sum {\omega^h_A}^2 \over \left (\sum \omega^h_A \right )^2} \right ) 
           + \left ( {\sum {\omega^e_A}^2 \over \left (\sum \omega^e_A \right )^2} \right ) 
           + \left ( {\sum {\omega^h_D}^2 \over \left (\sum \omega^h_D \right )^2} \right ) 
           + \left ( {\sum {\omega^e_D}^2 \over \left (\sum \omega^e_D \right )^2} \right ) }
\end{equation}
 and 
\begin{equation}
\begin{split}
\left ( \delta \left ( \Delta \langle P_\perp^2 \rangle \right ) \right )^2 = 
   \left ({{\sum \omega^h_A P_\perp^4 }\over{\sum \omega^h_A}} - \left ({\sum \omega^h_A P_\perp^2 }\over{\sum \omega^h_A}\right )^2 \right ) 
         \times \left ( {\sum \left ( {\omega^h_A}^2 \right ) \over \left ( \sum \omega^h_A \right ) ^2 }\right ) \\
 + \left ({{\sum \omega^h_D P_\perp^4 }\over{\sum \omega^h_D}} - \left ({\sum \omega^h_D P_\perp^2 }\over{\sum \omega^h_D}\right )^2 \right ) 
	 \times \left ( {\sum \left ( {\omega^h_D}^2 \right ) \over \left ( \sum \omega^h_D \right ) ^2 }\right ).
\end{split}
\end{equation}

@@

We present in figure \ref{fig:prelim} few preliminary results, before the application of any correction, with the goal to 
provide a first idea on data quality. The preliminary results will also be used to 
illustrate the effects of the corrections discussed below.

@@

To correct for acceptance effects, we simulated a total of a 100 million events 
per target ($^2$H, C, Fe and Pb) using the PYTHIA \cite{Sjostrand:2006za} 
event generator slightly modified to include Fermi motion effects. The 
generated events are processed by the CLAS software (GSIM, GPP and user\_ana) 
to simulate the detector and the reconstruction process similarly to the one for experimental data.

Then the simulated data are processed in a similar way than the experimental data by 
applying the cuts described in the section \ref{sec:pid}. Overall the 
simulation reproduces quite well the detectors responses, yet two issues might 
affect us and have to be understood. First, the efficiency of the CC is overestimated in the simulation. 
On the electron side the signal is a little stronger in the simulation (11 
photo-electrons) compared to experimental data (8 photo-electrons), but this 
feature should not affect us too much, because we are cutting only the tail of the 
distribution in both cases. For pion identification, as mentioned in section \ref{PiId},
we do not use the CC because of its unexpectedly low efficiency 
We observe, in the simulation, a much better detector response than in experiment 
(figure \ref{simPionCC} compared to figure \ref{PionCC}), this result also advocates against the use of the CC in the 
particle identification. Indeed, the poor reproduction of the experimental signal would introduce a bias in our acceptance correction. 
Second, in figure \ref{vertex} the cuts on vertex are shifted from one sector 
to another, since the simulation have perfect alignment of beam with CLAS this 
feature is not present in the simulated data. Therefore, we do not apply the 
shift from the table \ref{tab:vertex} to the simulation; results are shown in 
figure~\ref{simvertex}.

\begin{figure}[tpb]
\centering
\includegraphics[width=9cm] {chap5-fig/fig06simul.png} 
\caption {Histograms of momentum (GeV/c) of $\pi^-$ for {\bf simulated data}.
In black are all identified $\pi^-$, in red pions that also fire in the 
Cherenkov counter and in blue those that fire in the Cherenkov counter with 
more than one photo-electron.}
\label{simPionCC}
\end{figure}

@@

The weights ($\omega_{\pi^\pm}(\nu,x_{Bj},p_h,t)$) are then extracted from 
the simulation using equation \ref{eq:acc}, however, it appears that these should not be used directly.
Three factors are sources of problematic bins:
\begin{itemize}
 \item too large weight values, i.e. very small acceptance;
 \item very few events reconstructed, leading to large statistical errors;
 \item many events that were generated in another bin (bin migration).
\end{itemize}
To remove these bins we apply the following cuts:
\begin{equation} \label{eq:AccL1}
\left ({\delta \omega \over \omega}\right ) ^2 \times {R_c \over \omega} < 2,
\end{equation}
and
\begin{equation} \label{eq:AccL2}
N_{rec} > 4,
\end{equation}
with $\delta \omega / \omega$ the relative error on the weight and $R_c$ the 
proportion of events in the bin initially generated in another bin. Figure 
\ref{fig:AccCoef} shows the distributions of $\omega$, after the cuts. Around 
900 bins remain for both targets, but we notice that weights are much larger 
for $\pi^-$, indicating a larger correction, compared to $\pi^+$. In order to 
maximize the acceptance and reduce the sensitivity to the cuts applied on the 
weights, which are arbitrary, the bin weights are corrected. We apply a 
reweighting by calculating a new acceptance in a two dimensional binning:
\begin{equation}
\text{Acc}_2(\nu,p_h) = {\sum_{rec} \omega (\nu,x_{Bj},p_h,t)\over N_{gen}(\nu,p_h)}.
\end{equation}
with $\omega$ either the previously calculated weights or one for the 
excluded bins.
One of the criteria for setting the limits in equation \ref{eq:AccL1} and 
\ref{eq:AccL2} is to keep the reweighting factors $\omega_2 = 1/\text{Acc}_2$ at a few 
percents level.

@@

Figure \ref{fig:AcceptPlots}, where only statistical errors are 
represented, shows the new results after applying the acceptance correction.
The acceptance effects appear to be of $\sim 10$\% for multiplicity ratios and 
$\sim 30$\% for transverse momentum broadening. This is a surprisingly 
significant correction for the few centimeters between the two targets. The 
$\pi^-$s are more affected because of CLAS' magnetic field. Indeed, the low \pt
$\pi^-$s have very low acceptance, this makes the errors 
on \dpt very large and the related results difficult to exploit. Finally, because 
of some difference in position between the solid targets (table 
\ref{tab:targets}), some extra simulation is needed in order to exploit 
correctly the aluminum and tin results. Therefore, these two targets should not be considered for 
the final results.

@@

The radiative correction appears to be limited in amplitude in most of the 
kinematic, so we decided not to apply it before further studies. Improvement can 
be easily obtained by generating more statistics, in order to analyze the 
semi-inclusive effects in more depth. Also radiative effects from the target thickness 
are ignored in the current setup; these need to be evaluated and, eventually, 
corrected as well.

@@

The important excess of neutron in heavy nuclei leads to a modification of the 
$\pi$ multiplicity per DIS events. Using Hall~C results 
\cite{Asaturyan:2011mq}, shown in figure \ref{fig:IsoSpin}, we evaluate 
correction factors for this effect. Our simple estimation is solely based on 
proton and neutron numbers; the results for $\pi^+$s are shown in 
table~\ref{tab:isospin}. The effect on $\pi^-$ is found to be coherent with zero,
therefore no correction is applied for them. 
We attribute errors of 10\% of the effect for the isospin correction, this is chosen 
relatively to the precision of the Hall~C measurement.

@@

We finally note that the $A$ dependencies of the multiplicity ratios of the 
charged pions are similar after the isospin correction\footnote{Within 
normalization errors presented in section \ref{sec:TotSys}} (figure 
\ref{fig:IsoPlot}). Considering previous measurements and existing models, 
this result was expected and confirm the need for this correction to be applied.

@@

To evaluate those errors, we compare the reconstructed particles with the 
generated ones. Each reconstructed particle is associated with its generated parent using the
similarity in momentum and angle.
Distributions of $\Delta p$, $\Delta \theta$ and $\Delta \phi$ are defined as 
$\Delta x = {\sum_n |x_{gen} - x_{rec}| \over n}$. They give the precision with which we measure 
these variables. Using the same simulation than for the acceptance, we find 
${\delta p \over p } = 0.03$, $\delta \theta = 3$ mrad and 
$\delta \phi = 10$~mrad. These are broader than announced in \cite{Mecking:2003zu} 
but still reasonable. Then associated systematic errors can be easily 
evaluated for other variables: $\delta Q^2 \sim 0.013$ GeV$^2$/c$^2$, $\delta z \sim 
0.4 \%$, $\delta P_\perp^2 \sim 0.004$ GeV$^2$/c$^2$ and so on\footnote{These were 
evaluated for typical kinematics, the results can be significantly larger at 
extreme kinematics (large \pt or Q$^2$).}. These are negligible because they are 
several times smaller than our usual bin sizes (see figures in section 
\ref{prelim}).

We also evaluate particle misidentification and particles originating from 
scattering in the detector or the coils. Only tails of distributions can lead to high 
contamination by misidentification, the most problematic being the tail of the 
\pt distribution. This effect is due to the low probability to produce high 
\pt events, therefore the contribution from accidental is relatively 
increased. We use the following cut $p_\perp^2 < 2.5$~GeV$^2$/c$^2$, which 
only removes a very little amount of data ($\sim 1$ $\pi$ in 30000). The 
misidentification of electrons is found to be of the order of 1 in a 1000 and 
does not contribute significantly to the uncertainty. For pions, the main 
contamination comes from kaons above 2~GeV/c ($\sim$3\% of $\pi^+$ and 
$\sim$0.5\% of $\pi^-$). Incidentally, protons also contaminates $\pi^+$ at 
high momentum (up to few \%). The uncertainty related to 
misidentification is taken into account for the point to point systematic error 
evaluation, other effects are found to be negligible.

@@

Because of reconstruction errors or scattering on the detector materials, it 
is possible to associate a particle with the wrong target. To estimate this 
effect, we look, in the experimental data, at the number of events 
reconstructed upstream and downstream of the targets, where nothing should be
detected. We define two test regions (see figure \ref{fig:targetleak}) to evaluate
the contamination. The region 1 is upstream and chosen to be of the same size as the window used for solid 
target selection. We use it to evaluate contamination from the liquid target to the solid one. The region 2
is downstream and of the size of the window for the liquid target selection and allows to evaluate the solid target leak into the liquid one
The distance between detection and test regions is identical to the 
distance between the two detection regions.

@@

We apply two different acceptance corrections to the data using two different binnings 
(table \ref{tab:AcceptBinning}). The differences between them give us a good 
indication on the systematic error associated with the method. Using a sample 
of results from iron, we find the systematic presented in the table 
\ref{tab:SysAcc}. We note the significantly larger errors for $\pi^-$, which 
was expected because of the smaller acceptance and the larger weights. More 
significant are the large errors on the \dpt measurements, this is mainly due to 
the nature of the observable; as a difference \dpt enhances relative errors 
significantly. As was seen in figure~\ref{fig:AcceptPlots}, error bars are much 
larger for corrected \dpt indicating an important statistical 
sensitivity introduced by the weighting. The errors on \dpt are of the same 
order, or smaller, as the differences observed between the two sets. This is 
an indication that the uncertainties reported in table \ref{tab:SysAcc} are already 
taken into account in the statistical error.

@@

\subsubsection{Normalization Error}

The normalization errors -- i.e. independent of kinematic variables -- are due to acceptance effects, target identification 
and isospin correction. They are summarized in the table \ref{tab:sysid}.

>>>>

This chapter treats of the analysis of the data taken in CLAS for the 
experiments E-02-104 \cite{Brooks:2002aa} and E-02-110 \cite{Hafidi:2002aa}.
The code name for the run is {\it eg2}, it was composed of three phases 
labeled {\it a}, {\it b} and {\it c}. The analysis is performed on the data 
collected in the beginning of 2004 during the third phase ({\it eg2c}), for 
which the beam energy was 5.014~GeV\footnote{The other phases of the run gave only small 
amounts of data at a beam energy of 4~GeV that we decided not to use for this analysis.}.

@@

The analysis of the experiment E-02-110, focusing on the study of color 
transparency effects, has been approved and published~\cite{ElFassi:2008}. As this 
analysis went through a careful review by the CLAS collaboration, we use
similar analysis methods as much as possible. In particular, the electron selection 
presented here is very similar to theirs; the main difference being a new 
target determination method. The pion identification methods are however tightened
in this analysis as we have less constraints on the kinematics to exclude possible
contaminations.

@@

To select electrons, we also require that the particles are negatively charged, 
according to the bending direction of the tracks in the drift chamber.
Positively charged particles are identified as positrons. In the rest of the 
analysis we use events with only one electron and no positron to avoid any 
confusion between the scattered electron and electrons from hadronic decays or 
photon conversion.

@@

These cuts permit to minimize the kaon contamination, below 2.5~GeV/c, and the 
proton contamination for all momentum. The kaon contribution cannot be avoided, however 
it should remain a small contribution ($\sim$ 3\% according to simulation) 
with only a small effect on the final results (see section \ref{SysId} 
for details). Because protons could lead to even more contamination than kaons, 
a stricter cut is used at high momentum. This cut is also justified by 
HERMES data \cite{Airapetian:2007vu}, which show a very 
different behavior of the protons compared to the other hadrons.

@@

\begin{table}[p]
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Target & Carbon & Al (1) & Al (2) & Iron   & Tin    & Lead   \\ 
    \hline \hline
    Liquid & -30.1  & n/a    & n/a    & -30.2  & -30.1  & -30.1  \\ 
    Solid  & -24.7  & -25.0  & -23.8  & -24.9  & -23.8  & -24.9  \\
    \hline
  \end{tabular}
  \caption{Measured mean vertex position of targets, relative to the center of 
           CLAS (in cm). We note that aluminum data are separated in two sets because the 
           target position has brutally changed, moreover
           during these runs the deuterium target was empty.}
  \label{tab:targets}
\end{table}

@@

Since we are interested in deep inelastic scattering, we use the following 
cuts: $Q^2 > 1$~GeV$^2$/c$^2$ and $W > 2$~GeV. We also apply a cut $y < 0.85$ 
which corresponds to low energy electrons. These are removed beacause they are
significantly affected by radiative effects and at the limit of our trigger 
threshold.

@@

Once the identification is done, the calculation of the observables is 
straight forward with statistical errors given by:
\begin{equation}
{\delta \left ( R_A^h \right ) \over R_A^h} = \sqrt{ 1 /N_A^h + 1/ N_A^e +1/N_D^h + 1/N_D^e}
\end{equation}
and
\begin{equation}
\left ( \delta \left ( \Delta \langle P_\perp^2 \rangle \right ) \right )^2 = 
   \left ({\langle P_\perp^4 \rangle - \langle P_\perp^2 \rangle ^2}\right )_A / N_A^h
 + \left ({\langle P_\perp^4 \rangle - \langle P_\perp^2 \rangle ^2}\right )_D / N_D^h.
\end{equation}

However, the implementation of acceptance and radiative corrections is done through weights
given to each events depending on their kinematics. The multiplicity ratio then becomes
\begin{equation}
R_A^h (Q^2,\nu,z_h,P_\perp^2) = {{\sum \omega_A^h (Q^2,\nu,z_h,P_\perp^2) / \sum \omega_A^e (Q^2,\nu)} 
                       \over {\sum \omega_D^h (Q^2,\nu,z_h,P_\perp^2) / \sum \omega_D^e (Q^2,\nu)}},
\end{equation}
with $\omega$ the weights and all the sums running over all measured particles.
The expression for the transverse momentum broadening remains
\begin{equation}
\Delta \langle P_\perp^2 \rangle = \langle P_\perp^2 \rangle_A - \langle P_\perp^2 \rangle_D,
\end{equation}
but with
\begin{equation}
\langle P_\perp^2 \rangle = {\sum \left ( P_\perp^2 \times \omega (Q^2,\nu,z_h,P_\perp^2) \right ) \over \sum \omega (Q^2,\nu,z_h,P_\perp^2)}.
\end{equation}

This expressions leads to new expressions for the statistical error uncertainties taking weights into account: 
\begin{equation}
{\delta \left ( R_A^h \right ) \over R_A^h} = 
      \sqrt{ \left ( {\sum {\omega^h_A}^2 \over \left (\sum \omega^h_A \right )^2} \right ) 
           + \left ( {\sum {\omega^e_A}^2 \over \left (\sum \omega^e_A \right )^2} \right ) 
           + \left ( {\sum {\omega^h_D}^2 \over \left (\sum \omega^h_D \right )^2} \right ) 
           + \left ( {\sum {\omega^e_D}^2 \over \left (\sum \omega^e_D \right )^2} \right ) }
\end{equation}
 and 
\begin{equation}
\begin{split}
\left ( \delta \left ( \Delta \langle P_\perp^2 \rangle \right ) \right )^2 = 
   \left ({{\sum \omega^h_A P_\perp^4 }\over{\sum \omega^h_A}} - \left ({\sum \omega^h_A P_\perp^2 }\over{\sum \omega^h_A}\right )^2 \right ) 
         \times \left ( {\sum \left ( {\omega^h_A}^2 \right ) \over \left ( \sum \omega^h_A \right ) ^2 }\right ) \\
 + \left ({{\sum \omega^h_D P_\perp^4 }\over{\sum \omega^h_D}} - \left ({\sum \omega^h_D P_\perp^2 }\over{\sum \omega^h_D}\right )^2 \right ) 
	 \times \left ( {\sum \left ( {\omega^h_D}^2 \right ) \over \left ( \sum \omega^h_D \right ) ^2 }\right ).
\end{split}
\end{equation}

@@

We present in figure \ref{fig:prelim} few preliminary results, before the application 
of any correction, to 
provide a first idea on data quality. These preliminary results will also be used to 
illustrate the effects of the corrections discussed below.

@@

To correct for acceptance effects, we simulated a total of a 100 million events 
per target ($^2$H, C, Fe and Pb) using the PYTHIA \cite{Sjostrand:2006za} 
event generator slightly modified to include Fermi motion effects. The 
generated events are processed by the CLAS software (GSIM, GPP and user\_ana) 
to simulate the detector and the reconstruction process similarly to the one for 
experimental data.
% TODO GPP factors

Then the simulated data are processed in a similar way than the experimental data by 
applying the cuts described in the section \ref{sec:pid}. Overall the 
simulation reproduces quite well the detectors responses, yet two issues might 
affect us and have to be understood. First, the efficiency of the CC is 
overestimated in the simulation. 
On the electron side the signal is a little stronger in the simulation (11 
photo-electrons) compared to experimental data (8 photo-electrons), but this 
feature should not affect us too much, because we are cutting only the tail of the 
distribution in both cases. 
%For pion identification, as mentioned in section \ref{PiId},
%we do not use the CC because of its low efficiency.
%We observe, in the simulation, a much better detector response than in experiment 
%(figure \ref{simPionCC} compared to figure \ref{PionCC}), this result also 
%advocates against the use of the CC in the 
%particle identification. Indeed, the poor reproduction of the experimental 
%signal would introduce a bias in our acceptance correction. 
Second, in figure \ref{vertex} the cuts on vertex are shifted from one sector 
to another, since the simulation have perfect alignment of beam with CLAS this 
feature is not present in the simulated data. Therefore, we do not apply the 
shift from the table \ref{tab:vertex} to the simulation; results are shown in 
figure~\ref{simvertex}.

%\begin{figure}[tpb]
%\centering
%\includegraphics[width=9cm] {chap5-fig/fig06simul.png} 
%\caption {Histograms of momentum (GeV/c) of $\pi^-$ for {\bf simulated data}.
%In black are all identified $\pi^-$, in red pions that also fire in the 
%Cherenkov counter and in blue those that fire in the Cherenkov counter with 
%more than one photo-electron.}
%\label{simPionCC}
%\end{figure}

@@

The weights ($\omega_{\pi^\pm}(\nu,x_{Bj},p_h,t)$) are then extracted from 
the simulation using equation \ref{eq:acc}, however, it appears that these should not be used directly.
Three factors are sources of problematic bins:
\begin{itemize}
 \item too large weight values, i.e. very small acceptance;
 \item very few events reconstructed, leading to large statistical errors;
 \item large fraction of events originaly generated in another bin (bin migration).
\end{itemize}
To remove these bins we apply the following cuts:
\begin{equation} \label{eq:AccL1}
\left ({\delta \omega \over \omega}\right ) ^2 \times R_c \times \omega < 2,
\end{equation}
and
\begin{equation} \label{eq:AccL2}
N_{rec} > 4,
\end{equation}
with $\delta \omega / \omega$ the relative error on the weight and $R_c$ the 
proportion of events in the bin initially generated in another bin. Figure 
\ref{fig:AccCoef} shows the distributions of $\omega$, after the cuts. Around 
900 bins remain for both targets, but we notice that weights are much larger 
for $\pi^-$, indicating a larger correction, compared to $\pi^+$. In order to 
maximize the acceptance and reduce the sensitivity to the cuts applied on the 
weights, which are arbitrary, the bin weights are corrected. We apply a 
reweighting by calculating a new acceptance in a two dimensional binning:
\begin{equation}
\text{Acc}_2(\nu,p_h) = {\sum_{rec} \omega (\nu,x_{Bj},p_h,t)\over N_{gen}(\nu,p_h)}.
\end{equation}
with $\omega$ the previously calculated weights or one for the 
bins excluded by the cuts.
One of the criteria for setting the limits in equation \ref{eq:AccL1} and 
\ref{eq:AccL2}is to keep the reweighting factors $\omega_2 = 1/\text{Acc}_2$ at a few 
percents level.

@@

Figure \ref{fig:AcceptPlots}, where only statistical errors are 
represented, shows the new results after applying the acceptance correction.
The acceptance effects appear to be of $\sim 10$\% for multiplicity ratios and 
$\sim 30$\% for transverse momentum broadening. This is a surprisingly 
significant correction for the few centimeters between the two targets. The 
$\pi^-$s appears to be more affected. This is due to the inbending magnetic 
field. Indeed, the low \pt $\pi^-$s have very low acceptance, leading to large 
correction factors. The large spread in weights makes the errors 
on \dpt very large and the related results difficult to exploit. 
On the bright side, after the correction, the transverse momentum
broadening of both pions now match.

@@

The semi-inclusive part of the radiative correction appears to be limited 
in amplitude in most of the 
kinematic, except for high $z$ and \ptp. So, we decided not to apply this 
correction before further studies.

{\color{red} We found a better way to implement the radiative correction,
that is not limited by the Monte-Carlo technique. We will implement it in
the second version of the note as we do not want to delay the review process for
this correction that we already found to be small. Sorry about that.}

@@

The important excess of neutrons in heavy nuclei leads to a modification of the 
$\pi$ multiplicity per DIS events. Using Hall~C results 
\cite{Asaturyan:2011mq}, shown in figure \ref{fig:IsoSpin}, we evaluate 
correction factors for this effect. Our simple estimation is solely based on 
proton and neutron numbers; the results for $\pi^+$s are shown in 
table~\ref{tab:isospin}. The effect on $\pi^-$ is found to be coherent with zero,
therefore no correction is applied for them. 
We attribute errors of 10\% of the effect for the isospin correction, this is chosen 
relatively to the precision of the Hall~C measurement and the fact that they do not 
cover as much phase space as we do.

@@

We finally note that the $A$ dependencies of the multiplicity ratios of the 
charged pions are parallel after the isospin correction\footnote{Within 
normalization errors presented in section \ref{sec:TotSys}} (figure 
\ref{fig:IsoPlot}). Considering previous measurements and existing models, 
this result was expected and confirm the need for this correction to be applied.

@@

To evaluate those errors, we compare the reconstructed particles with the 
generated ones. Each reconstructed particle is associated with its generated parent using the
similarity in momentum and angle.
Distributions of $\Delta p$, $\Delta \theta$ and $\Delta \phi$ are defined as 
$\Delta x = {\sum_n |x_{gen} - x_{rec}| \over n}$. They give the precision with which we measure 
these variables. Using the same simulation than for the acceptance, we find 
${\delta p \over p } = 0.03$, $\delta \theta = 3$ mrad and 
$\delta \phi = 10$~mrad. These are broader than announced in \cite{Mecking:2003zu} 
but still reasonable. Then associated systematic errors can be easily 
evaluated for other variables: $\delta Q^2 \sim 0.013$ GeV$^2$/c$^2$, $\delta z \sim 
0.4 \%$, $\delta P_\perp^2 \sim 0.004$ GeV$^2$/c$^2$ and so on\footnote{These were 
evaluated for typical kinematics, the results can be larger at 
extreme kinematics (large \pt or Q$^2$).}. These are negligible because they are 
several times smaller than our usual bin sizes (see figures in section 
\ref{prelim}).

We also evaluate particle misidentification and particles originating from 
scattering in the detector or the coils. Only tails of distributions can lead to high 
contamination by misidentification, the most problematic being the tail of the 
\pt distribution. This effect is due to the low probability to produce high 
\pt events, therefore the contribution from accidental is relatively 
increased. We use the following cut $p_\perp^2 < 2.5$~GeV$^2$/c$^2$, which 
only removes a very little amount of data ($\sim 1$ $\pi$ in 30000). The 
misidentification of electrons is found to be of the order of 1 in a 1000 and 
does not contribute significantly to the uncertainty. For pions, the main 
contamination comes from kaons above 2~GeV/c ($\sim$3\% of $\pi^+$ and 
$\sim$0.5\% of $\pi^-$). Protons also contaminates $\pi^+$ at 
high momentum (up to few \%). 
%TODO Justify the pt cut with a figure?

In conclusion, the uncertainty related to misidentification 
is taken into account at the level of 100\% of the contamination in the point 
to point systematic errors, other effects are found to be negligible.

@@

Because of reconstruction errors or scattering on the detector materials, it 
is possible to associate a particle with the wrong target. To estimate this 
effect, we look, in the experimental data, at the number of events 
reconstructed upstream and downstream of the targets, where nothing should be
detected. We define two test regions (see figure \ref{fig:targetleak}) to evaluate
the contamination. The region 1 is upstream and chosen to be of the same size as the window used for solid 
target selection. We use it to evaluate contamination from the liquid target to the solid one. The region 2
is downstream and of the size of the window for the liquid target selection 
and allows to evaluate the solid target leak into the liquid one.
The distance between detection and test regions is identical to the 
distance between the two detection regions.

@@

We tested several different acceptance corrections to the data using finally 
two different binnings 
(table \ref{tab:AcceptBinning}). The differences between them give us a good 
indication on the systematic error associated with the method. Using our
results on iron, we find the systematic presented in the table 
\ref{tab:SysAcc}. We note the significantly larger errors for $\pi^-$, which 
was expected because of the smaller acceptance and the larger weights. More 
significant are the large errors on the \dpt measurements, this is mainly due to 
the nature of the observable; as a difference \dpt enhances relative errors 
significantly. As was seen in figure~\ref{fig:AcceptPlots}, error bars are much 
larger for corrected \dpt indicating an important statistical 
sensitivity introduced by the weighting. The errors on \dpt are of the same 
order, or smaller, as the differences observed between the two sets. This is 
an indication that the uncertainties reported in table \ref{tab:SysAcc} are 
similar in nature with the statistical error, in the sense that they originate
from the large variation between the weights from event to event. For this
reason, we decide not to include this error in order to double count it.

@@

\subsubsection{Total Error}

The point to point errors include the contributions from detection 
contamination and acceptance effects. The normalization errors 
-- i.e.~independent of kinematic variables -- are due to acceptance effects, 
target identification and isospin correction. They are summarized in the 
table~\ref{tab:sysid}.
